Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-09-14 paper/paper.tex
Move methods to end and remove conclusion
Move survey discussion to separate section

@@

These human similarity judgments are obtained from a set of $78$ instrument--IPT pairs selected by two music composition professors at the \emph{Conservatoire national sup\'erieur de musique et de danse de Paris} (CNSMDP).
A subject was provided with these 78 recordings and asked to cluster them in a free sorting task by arranging correspodings dots in two dimensions on a computer screen and assigning a color to each dot.
While the location of the dots was recorded, this information was not used in our analysis and only served to help the subject organize the sounds spatially.
The colors assigned to each dot---and, consequently, to each sound---was recorded for each subject.

Given the clustering assignments of each subject, we then constructed a consensus clustering using a hypergraph partitioning algorithm \cite{kernighan1970efficient,han1997scalable,strehl2002cluster}.
Interestingly, although several sounds pairs were obtained from the same instrument (but different IPTs) and others were obtained using the same IPT (but different instruments), the consensus clustering did not favor one of these taxonomies over the other.

@@

\section*{Conclusion}
\label{sec:conclusion}

>>>>

\subsection*{Timbre similarity perception}
\label{sec:survey}

To validate our timbre perception model, we first acquired similarity judgments from a survey of human subjects.
The survey was carried out for $78$ sounds, each representing an instrument--playing technique (IPT) pair.
These IPTs were selected from a larger set of $235$ IPTs by two experts at the \emph{Conservatoire national sup\'erieur de musique et de danse de Paris} (CNSMDP).
The selection criteria were based on the likelihood of an IPT being similar to some other IPT, ensuring that IPTs that were too singular were excluded from the survey.

In the survey, a subject was provided with these $78$ IPTs at the same pitch and asked to cluster them in a free sorting task.
This was achieved by arranging correspoding dots in a two-dimensional plane on a computer screen and assigning a color to each dot.
While the location of the dots was recorded, this information was not used in our analysis and only served to help the subject organize the sounds spatially.
The colors assigned to each dot---and, consequently, to each sound---was recorded for each subject.

Given the clustering assignments of each subject, we then constructed a consensus clustering using a hypergraph partitioning algorithm \cite{kernighan1970efficient,han1997scalable,strehl2002cluster}.
Interestingly, although several sounds pairs were obtained from the same instrument (but different PTs) and others were obtained using the same PT (but different instruments), the consensus clustering did not favor one of these taxonomies over the other.

@@

@@
